HGP analysis

### 2019-03-01 rick/1KGP.Rmd
update

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)
library(furrr)
options(future.globals.maxSize= 10000000000)
plan(multicore)
```

@@

@@

```{r}
# Convert to a sparse matrix of people (rows) x variant (columns)
chr20 <- sparseMatrix(i=x[,2], j=x[,1], x=1.0)

@@

```{r}
chr20_mtx <- t(as.matrix(chr20_sub))
```

@@

```{r}
ggplot(bas_dt,
       aes(lf1, lf2, color=Population)) +
  geom_point() +
  theme_bw()
```

@@

to_datalist <- function(i, data_genotype, data_iaf, qual){

    data <- tibble(genotype=data_genotype[i,],
               iaf=data_iaf[i,],
               qual=qual)

@@

fit_model_1 <- function(data){

@@

plot_data <- function(data){

@@

data_list <- map(loci, 
                 to_datalist,
                 data_genotype=chr20_mtx,
                 data_iaf=chr20sub_ial,
                 qual=bas_dt$avg_qual_mean)

@@

```{r}
fits <- future_map(data_list, fit_model_1)

```{r}
plots <-  future_map(data_list, plot_data) 
```

>>>>

```{r}
library(Matrix)
library(irlba)
library(threejs)
library(tidyverse)
library(lfa)
library(furrr)
library(broom)
options(future.globals.maxSize= 10000000000)
plan(multicore)
```

@@

```{r}
bas_dt<- read_tsv( "average_quality_chrom21.txt")
```

@@

```{r}
# Convert to a sparse matrix of people (rows) x variant (columns)
chr20 <- sparseMatrix(i=x[,2], j=x[,1], x=1L)

@@

```{r}
chr20_mtx <- t(as.matrix(chr20[,1:100000]))
```

@@

```{r}
ggplot(bas_dt,
       aes(lf2, lf3, color=Population)) +
  geom_point() +
  theme_bw()
```

@@

to_datalist <- function(i, data_genotype, data_iaf){

    data <- tibble(genotype=data_genotype[i,],
               iaf=data_iaf[i,])

@@

fit_model_1 <- function(data, qual){

@@

plot_data <- function(data,qual){

@@

data_list <- map(loci, 
                 to_datalist,
                 data_genotype=chr20_mtx,
                 data_iaf=chr20sub_ial)

@@

```{r}
data_list <- enframe(data_list,
                     name = "locus", 
                     value = "dataset")
```

```{r}
avg_qual_mean <- bas_dt$avg_qual_mean
data_list <- 
  data_list %>%
  mutate(
    fit = future_map(dataset,~ glm(genotype ~ avg_qual_mean + offset(iaf), family ="binomial", data=.x)),
    tidied = future_map(fit, tidy),
    glanced = future_map(fit, glance)
)
```

get all p-values
```{r}
p_values_dt <-
  data_list  %>% 
  select(tidied) %>% 
  map_depth( 2, "p.value") %>% 
  map_depth( 2, c(2)) %>% # c(1) for the intercept
  unlist(use.names = FALSE) %>% 
  enframe(name = "locus" ,
          value= "p.value")%>%
  mutate(locus= data_list$locus)

p_values_dt
```
get a p-value for target specific loci

```{r}
target_loci <- c("4", "5")
```

```{r}
p_values_subset <-
  data_list  %>% 
  filter(locus %in% target_loci) %>% 
  select(tidied) %>% 
  map_depth( 2, "p.value") %>% 
   map_depth( 2, c(2)) %>%
  unlist(use.names = FALSE) %>% 
  enframe(name = "locus" ,
          value= "p.value")%>%
  mutate(locus= target_loci)
p_values_subset 
```
